resistanceModelNotesAndy

### 2015-04-30 resistanceModelNotesAndy.Rmd
progress notes

```{r}
require(devtools)    
install_github('AndySouth/resistance') 
library(resistance)
resistanceMaster(params.csv = FALSE)
```

@@

```{r}
out <- sensiAn1( nScenarios = 10, h.RS1_A0=c(0.1,1))
```

@@

**29/4/15** 10.30-12.30 2hrs 3.15-

working on refactoring variables to arrays

@@

1. before May 15th move Spark and Glimmer shiny apps

@@

#to fill al elements as above
W <- 0.1
#check length
length(W)
#to access one element
W['m','SS1','RR2']
#to check that males total 1
sum(a['m',,])
```

>>>>

```{r}
#require(devtools)    
#install_github('AndySouth/resistance') 
library(resistance)
resistanceMaster(params.csv = FALSE)
```

@@

```
out <- sensiAn1( nScenarios = 10, h.RS1_A0=c(0.1,1))
```

@@

**29/4/15** 10.30-12.30 2hrs 3.15-5.15 4hrs

#to fill al elements as above
W[] <- 0.1
#check length
length(W)
#to access one element
W['m','SS1','RR2']
#to check that males total 1
sum(W['m',,])
```

working on refactoring variables to arrays, made flexible createArray() function.
good progress
started runModel2() to contain the refactoring

**30/4/15** 9.45-

Need to be careful about different W fitness variables
`W.RR1_00 : [locus][niche]` single locus (Wlocus)
`W.RR1SS2_0b :   [locus1][locus2][niche]` niche (Wniche)
`W.m.SS1SS2 : [sex][locus1][locus2]` sex (Windiv)

Once I have array refactoring working by .
```{r}

    a <- createArray( sex=c('m','f'), niche1=c('0','a','A'), niche2=c('0','b','B') )
    Wniche <- createArray( locus1 = c('SS1','RS1','RR1'), locus2 = c('SS2','RS2','RR2'), niche1=c('0','a','A'), niche2=c('0','b','B') )    
    Windiv <- createArray( sex=c('m','f'), locus1 = c('SS1','RS1','RR1'), locus2 = c('SS2','RS2','RR2') )
```
I should be able to replace 
```
    W.m.SS1SS2 <- (a.m_00 * W.SS1SS2_00) + 
      (a.m_a0 * W.SS1SS2_a0) + (a.m_A0 * W.SS1SS2_A0) + 
      (a.m_0b * W.SS1SS2_0b) + (a.m_0B * W.SS1SS2_0B) + 
      (a.m_ab * W.SS1SS2_ab) + (a.m_AB * W.SS1SS2_AB) + 
      (a.m_Ab * W.SS1SS2_Ab) + (a.m_aB * W.SS1SS2_aB) 
```
with
```{r}
    Windiv['m','SS1','SS2'] <- sum( a['m',,] * Wniche['SS1','SS2',,])
```
To prove that the above works
```{r}
    #set constant
    a['m',,] <- 2 
    #set variable
    Wniche['SS1','SS2',,] <- 1:9
    Wniche['SS1','SS2',,]

    #showing that each element gets multiplied by 2
    a['m',,] * Wniche['SS1','SS2',,]

    #show result of sum
    sum( a['m',,] * Wniche['SS1','SS2',,])

    Windiv['m','SS1','SS2'] <- sum( a['m',,] * Wniche['SS1','SS2',,])

```
Gives a result of 90 for just mSS1SS2 which is correct
``` Windiv
, , locus2 = SS2

   locus1
sex SS1 RS1 RR1
  m  90   0   0
  f   0   0   0

, , locus2 = RS2

   locus1
sex SS1 RS1 RR1
  m   0   0   0
  f   0   0   0

, , locus2 = RR2

   locus1
sex SS1 RS1 RR1
  m   0   0   0
  f   0   0   0
```

Or indeed might be able to replace the whole 120 lines of code from 510-630 with :
No these give: 
```
#Error in a[, , ] * Wniche[, , , ] : non-conformable arrays
    Windiv['m',,] <- sum( a['m',,] * Wniche[,,,])
    Windiv['f',,] <- sum( a['f',,] * Wniche[,,,])
    #or even just
    Windiv[,,] <- sum( a[,,] * Wniche[,,,]) 
```
Just needs a little more thought ...
It's because a needs to be applied repeatedly to each genotype.
Maybe worry about that later ..

Want to develop a sequential testing process, so that I can compare runModel() and runModel2().
Maybe I could use testthat for it ?

Just need to do this to start :
`devtools::use_testthat()`

see testRefactoring() which does things like this :

```
input <- setInputOneScenario()
tst <- runModel(input)
tst2 <- runModel2(input)
input <- setInputSensiScenarios(20, h.RS1_A0=c(0.1,1), h.RS2_0B=c(0.1,1), s.RR1_A0=c(0.2,1), s.RR2_0B=c(0.2,1))
tst <- runModel2(input, produce.plots=FALSE)
tst2 <- runModel(input, produce.plots=FALSE)
identical(tst,tst2)
```

@@

1. before May 15th move Spark and Glimmer shiny apps
1. I should have included unit testing on my CV

@@
